### 2016-05-05 ch05-initvals/initial-values.tex
Add thumb index
Revert "Add thumb index"
This reverts commit 18177995b597a30e5df7c5f1278b7fb207af0692.
It does include some small fixes here and there (so not a full revert)
(sub)+sections: title case + some \gls{...}

\chapter{Initialization of parametric estimators}
\label{sec:initvals}
\myEpigraph{Everything starts somewhere, though many physicists disagree. But people have always been dimly aware of the problem with the start of things. They wonder how the snowplough driver gets to work, or how the makers of dictionaries look up the spelling of words.}{Terry Pratchett}{Hogfather}
\gdef\thisDir{ch05-initvals}
\tikzsetfigurename{ch05fig}
\researchBasedOn{Geerardyn2015TIM}

@@

\section{Problem formulation}
\label{sec:initial-values:ProbForm}

@@

\begin{remark}
Note that methods 3) and 4) result in a non-parametric estimate of the transfer function, represented as the \gls{FRF}. 
A corresponding parametric estimate is obtained as follows. 
A parametric estimator (\gls{GTLS}, \gls{BTLS}, and \gls{MLE}) is invoked, where the input spectrum is considered to be $1$ at all frequencies (Dirac in the time domain), and the output spectrum is set equal to the estimated \gls{FRF} $G_{\bullet}(\omega_k)$, with the transient term $I$ set to zero:
\begin{equation}
  U_{\mathrm{FRF}}(\omega_k) \isdef 1 
  \qquad \text{and} \qquad
  Y_{\mathrm{FRF}}(\omega_k)  \isdef G_{\bullet}(\omega_k)
  \text{.}
\end{equation}
It is important to note that invoking the \gls{GTLS}, \gls{BTLS} and \gls{MLE} on the \glspl{FRF} from methods 3) and 4) will yield a different result from applying the \gls{GTLS}, \gls{BTLS} and \gls{MLE} on the raw data. 
This is because the \glspl{FRF} from 3) and 4) have been smoothed and, thus, have a significantly reduced noise variance.
\end{remark}
%}

%\comment{JL: one could remove the subsection below (why? see my comments below), and mention that the the above initial estimates are then fed to the MLE, with the raw data, to obtain the final estimates.}

%\subsection{Genesis of the Initial Estimates} 
%\comment{JL: why `genesis'? This section is actually where you use the initial estimates, not their origin.}
%{Deploying the initial estimates}

%\comment{ML: Fig. \ref{fig:flowgraph} should include an additional path for RFIR/RARX, and the accompanying text (below) is to be modified accordingly.}
%Fig. \ref{fig:flowgraph} shows a flowchart for the MLE implementation, using four sets of initial values consisting of the known raw input/output data, plus: \comment{JL: is it really required to repeat the content of the flowchart? It has actually been explained in further details in \secref{sec:init:procedures}.}
%\begin{enumerate}
%\item (Left (first) path of the flowchart): The true model $\true{G}$ as initial values,
%\item (Second path from the left of the flowchart): Initial values obtained from \emph{existing} initial estimate strategies, namely GTLS (generalized total least squares) and BTLS (bootstrapped total least squares),
%\item (Third path from the left of the flowchart): The LPM-truncated initial values with BTLS and GTLS, and  
%%\item (Right (fourth) path of the flowchart): The RFIR initial values with BTLS and GTLS.  
%\end{enumerate}

%\JL{
%The main contribution of this paper is to demonstrate that $\model{trunc}$ (third path) yields an improvement over $\model{exist}$ (second path). \comment{JL: these symbols haven't been introduced yet. I'm getting quite confident that this subsection can be removed.}The quantification of this improvement is formally introduced in the next section.
%}

%The latter 2 ....schematic is configured to include connections of the initial values and the input to the LPM block and/or to the MLE block(s) for estimation purposes.
%\end{itemize}
%\section{Example}\label{sec:initial-values:Example}

\subsection{Success Rates of the Initial Estimates}

The initial estimates described above are then fed to the MLE together with the raw data to obtain the final estimates.

Formally, let $\model{\bullet}$ be the final parametric estimate of the system, where the subscript $\bullet$ denotes the methods (from left to right in Fig.~\ref{fig:flowgraph}) when an initial estimate $\model[init]{\bullet}$ is used, \emph{viz}:
\begin{itemize}
    \item $\model{\trueSymbol}$ via the true model $\true{G}$ as an initial estimate,
    \item $\model{exist}$ is obtained via GTLS and BTLS,
    \item $\model{trunc}$ by the use of the LPM with truncation as an initial estimate,
    \item $\model{RFIR}$, initialized by means of the RFIR method. 
\end{itemize}

A particular initial estimate is deemed \emph{successful} if the optimization of the MLE cost with the raw input-output data inserted in equation~\eqref{eq:MLEcf}, approximately reaches the \emph{best local optimum} when iteration is initiated with the selected initial value/estimate.

@@

Both systems are low-pass Chebyshev filters which have been generated using the \MATLAB command \mcode[mathescape]{cheby1(2, $\,Q$, 0.05)}.
Their transfer functions are shown in \figref{fig:exampleFRF}.
Their inputs are excited by zero mean white Gaussian noise with unit variance, and the outputs are disturbed by different realizations of white gaussian noise, as in \figref{fig:oesetup}, with a variance $\sigma_v^2$, such that a prescribed \gls{SNR} defined as
\begin{equation}
  \mathrm{SNR} 
    = \frac{\sigma_v}
           {\rms{y_0}}
    \approx \frac{\sigma_{v}}
                 {\left\| \true{G} \right\|_2 \rms{u_0}}
    =  \frac{\sigma_{v}}
            {\left\| \true{G} \right\|_2}
  \label{eq:SNR-definition}
  \text{.}
\end{equation}
is attained.
$\rms{x} = \sqrt{N^{-1} \sum_t x^2(t)}$ denotes the root-mean-squared value of $x$.
%}%}

%\JL{
%\subsection{Successful VS failed estimation}
\subsection{Comparison of Successful and Failed Estimates}

%Referring to \figref{fig:exampleFRF}, 4 FRFs are shown: $\true{G}$, $\hat \true{G}$, one successful $\hat G_\bullet$ and one failed $\hat G_\bullet$.
%}
%\EG{
 \figref{fig:exampleFRF} depicts the Bode plot of the actual system $\true{G}$, in black
%\comment{JL: in what color? (EG) black},
 and different estimates $\model{exist}$
 %\comment{JL: does it matter whether it is $\model{exist}$ or any other $\hat G_\bullet$? (EG) No, other methods will have similar results} 
 that may or may not approximate $\model{\trueSymbol}$ well, according to the distance defined by equation \eqref{eq:successrateTol}.
 The systems shown here are drawn randomly from the successes and failures observed in the Monte Carlo simulations, which are discussed later on in this chapter.

 It is clear from \figref{fig:exampleFRF} that the successful estimates virtually coincide with the true system. This means 
that their distances from the true system, e.g. as given by $\norm[2]{\model{\bullet} - \true{G}}$, have small values. 
On the other hand, the `failed' estimates are inaccurate descriptions of the true system. It is apparent that their associated distances from the true system are larger by, at least, an order of magnitude than for the successful estimates.
   %Given the 2-norm \eqref{eq:successrateTol} employed 
   %Using the 2-norm in equation \eqref{eq:successrateTol} to classify `successes' and `failures', it can be observed that the `successes' approximate $\hat{G}_0$ well w.r.t. the relative error, except when $\abs{\true{G}(\omega)}$ is small.
 %Practically, 
 %In practice, this means that a successful estimate provides reasonable estimates of the pass-band of the system, but may perform poorly in the stop-band. \comment{Further discussion required: what about the absolute error? Isn't it more or less white over the complete frequency band?} \ML{To be discussed}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{0.6\figurewidth}
  \input{\thisDir/figs/exampleSystems.tikz}
 % \caption{Results of an example of Monte Carlo simulation.}
 \caption[Bodeplot of successful ad failed estimates.]{Illustrative Bode plots of a few successful~\legref{leg:example-good-estimate} and `failed'~\legref{leg:example-bad-estimate} estimates $\model{\bullet}$ for both systems $\true{G}$~\legref{leg:example-exact} under test.
 The `failed' estimates are caused by local minima in the cost function.
 Success or failure is determined using the criterion in equation~\eqref{eq:successrateTol}. The $3\unit{dB}$ bandwidth of each system is highlighted~\legref{leg:example-3db-bandwidth}.}
\label{fig:exampleFRF}
\end{figure}

%\subsection{Computing the success rates}
\subsection{Computation of  the Success Rates}\label{sec:initial-values:CompuSR}

@@

\subsection{Identification procedure}
The repeated nature of the experiment makes it possible to estimate the noise level from the signals non-parametrically.
The mean signal from the input $u$ is of the form:
\begin{equation}
  \tilde{u}(t) = \frac{1}{N_R} \sum_{r=1}^{N_R} u^{[r]}(t)
\end{equation}
Thus, the reduced noise influence and the approximate noise co-variances are, respectively:
\begin{align}
  \hat\sigma_{u}^2(t) &= \frac{1}{N_R - 1} 
                    \sum_{r=1}^{N_R} 
                    \left( u^{[r]}(t) - \tilde{u}(t) \right)^2 \\
%and the noise co-variances are approximately
  \hat\sigma_{yu}(t) &= \frac{1}{N_R - 1} 
                    \sum_{r=1}^{N_R} 
                    \left( y^{[r]}(t) - \tilde{y}(t) \right)
                    \overline{\left( u^{[r]}(t) - \tilde{u}(t) \right)}
  \label{eq:variancePeriodic}            
\end{align}

@@

\subsection{Reference model measurements}

@@

\subsection{Model estimation}
  The measurements on the NI Elvis II indicate that the high-quality starting value $G_{\mathrm{VXI}}$ led to low cost function values as shown in \figref{fig:costMeasurements} and \tabref{tbl:costMeasurements}.
  The existing methods exhibit a high spread and a high median cost function, showing that a good estimate is obtained only in about $25\%$ of the cases.
  The truncation method provides better estimates in many cases, but still suffers from a high variability.
  On the other hand, the \gls{RFIR}-based initial values have both a low median cost function and spread, and thus provide better fits in almost all cases.
  Obviously, $\model{best}$ has the lowest cost function values of all methods.
  The similarity of the results for $\model{RFIR}$ and $\model{best}$ suggests that the \gls{RFIR} provides the best estimate in most of the cases.
  This can indeed be confirmed by inspecting the different estimates per repetition of the experiment.

@@

\subsection{Model validation}
\subsubsection{Cost function limitations}
In the previous section, the cost function was studied to determine the effectiveness of the starting values.
However, inspecting the cost function $V(\theta)$ only accounts for how well an estimated model fits the measured data, which may be misleading.
For an example, overfitting a model may result in the absorption of both the systematic behavior and the noise into the model. 
Consequently, an arbitrarily small cost function may ensue although the estimated model may be virtually useless to predict the system behavior.

\subsubsection{Validation criterion}
To objectively assess the quality of an estimated model, a different criterion than the cost function is inspected.
To this end, the model is validated using the 2-norm (or distance) on the model error:
\begin{equation}
  \validationDistance{\bullet} 
  \isdef 
  \norm[2]{\model{\bullet} - G_{\mathrm{VXI}}}
  \text{.}
  \label{eq:measurementCriterion}
\end{equation} 
This criterion indicates how well the obtained estimates $\model{\bullet}$ are able to describe the transfer function of the bandpass filter as observed in the validation measurement on the \gls{VXI}.

\subsubsection{Validation performance}
The observed median and \gls{IQR} of the distances in \figref{fig:validationMeasurements} and \tabref{tbl:validationMeasurements} have a similar qualitative interpretation as the cost function on the estimation data.
The existing methods provide good estimates in only $25\%$ of the cases.
The truncation method provides a considerable improvement but still suffers from $25\%$ poor estimates.
Compared to the existing \gls{BTLS} and \gls{GTLS} techniques, the \gls{RFIR} and hence also $\model{best}$ entail an overall reduction in the observed distance by a factor $8$, in most cases. 
On the other hand, the reference $\model{VXI}$ shows the best global performance. 
This indicates that the proposed methods do no converge to the same local optimum.
Nevertheless, the proposed methods improve the model quality by almost an order of magnitude.

@@

\section{Consequences of selecting the `best` model}
To determine how important it is to retain the `best' model based on the cost function values, we shall inspect how much worse (or better) the second best model $\model{2nd}$ performs when $\model{best}$ is \emph{not} selected.
To do so, we inspect the performance by means of the cost function (used during estimation) and by means of the validation distance.
The datasets used in this analysis are those from the measurements, but similar results can be obtained from the other data sets.

@@

\section{Remark on the generality}
\label{sec:initial-values:Generality}
In the previous sections, the usability of the smoothers to produce initial values has been studied on very specific examples.
In this section, an attempt will be made to illustrate the usefulness of these smoothers for the generation of starting values for other systems.
However, due to the intricate relationship between the attraction regions in the cost function, the location of the actual system poles, the \gls{SNR} level and the choice of a particular excitation signal, we think it is intractable to construct rigid bounds on where the smoothers produce effective starting values.

\subsection{Limitations of the smoothers}
On the one hand, an obvious limitation to the presented initialization techniques is that they share the limitations of the smoothing techniques: if the non-parametric estimate is a worse representation than the raw data (e.g. heavily biased), it is very unlikely that the initial estimate will outperform the existing estimates.
However, it is beyond the scope of this chapter to determine formally which particular smoother is optimal in some specific experimental circumstances.

@@

\subsection{Stress test of the smoothers}
To test the effectiveness of the initial estimates obtained from these particular smoothers, an extra set of $n_{\mathrm{MC}} = 100$ Monte Carlo simulations were performed.
In particular, all combinations of
\begin{itemize}
  \item low-pass, high-pass, band-pass and band-stop 
  \item Chebyshev Type I, Chebyshev Type II, Elliptical and Butterworth
\end{itemize}
discrete-time filters~\citep{Zverev1967} of tenth degree generated by the \MATLAB code in \lstref{lst:initvals:stressSystems} are simulated.
Each of these filters $\true{G}$ have been normalized such that $\norm[2]{\true{G}} = 1$.
The low-pass and high-pass filtes have a cross-over frequency of $\frac{\pi}{2} \unit{rad/s}$. 
The band-pass, respectively band-stop, filters have a passband, respectively stopband, in the frequency range$\left[ \frac{2\pi}{5}, \frac{3\pi}{5}\right] \unit{rad/s}$.
Note also that both the band-pass and band-stop filters have a McMillan degree of 20 as per the \MATLAB conventions.
See \tabref{tbl:init:stresstest} for an overview of the filters and  \figref{fig:bodeplots} for the corresponding bode plots.

@@

\section{Computational effort}\label{sec:initvals:computation}
While improved initial values yield better models of an improved quality, their generation does require some computational effort.
Although the amount of available computing power has been steadily increasing over the last decades, it remains important to keep an eye on the computing effort required to estimate a model or, in this case, to generate the starting values required to estimate a model.
E.g. in the field of embedded processors, which has been attracting a lot of attention over the last few years leading to ``Internet of Things'', it remains an important factor since computing power and physical power consumption are still relatively scarce.

@@

\subsection{Practical runtime}
In practical measurements of the computation time for any piece of software, one typically distinguishes between different kinds of `time'.
\begin{itemize}
  \item The wall-clock time $\wallclocktime$, sometimes called `real time`, is the time difference between the start and end of the program under test.
  \item The \glsentryshort{CPU} time $\cputime$, is the amount of time that the \glspl{CPU} actually spends executing the program under test.
\end{itemize}
This distinction is necessary for multi-tasking environments (such as computer), since during the execution of the program under test, the \gls{CPU} may spend a while to execute other programs in the background.
The latter obviously requires a small amount of wall-clock time, but it does not increase the \gls{CPU} time of the program:
\begin{equation}
  \wallclocktime = \cputime + t_{\mathrm{other\;processes}}
\end{equation}
for a single-core \gls{CPU}.

@@

\subsection{Asymptotic runtime}
For the asymptotic runtime, we are mainly interested in how the runtime of the smoothers scale with the size of the dataset, i.e. the number of samples $N$, and the model complexity $n_{\theta}$ of the smoother.

@@

\subsection{Implementation aspects}
This section presents some implications and recommendations for the implementation of  a system identification toolbox.

>>>>

\chapter{Initialization of Parametric Estimators}
\label{sec:initvals}
\myEpigraph{Everything starts somewhere, though many physicists disagree. But people have always been dimly aware of the problem with the start of things. They wonder how the snowplough driver gets to work, or how the makers of dictionaries look up the spelling of words.}{Terry Pratchett}{Hogfather}
\gdef\thisDir{ch05-initvals}
\tikzsetfigurename{ch05fig}
\researchBasedOn{Geerardyn2015TIM}

@@

\section{Problem Formulation}
\label{sec:initial-values:ProbForm}

@@

\begin{remark}
Note that methods 3) and 4) result in a non-parametric estimate of the transfer function, represented as the \gls{FRF}. 
A corresponding parametric estimate is obtained as follows. 
A parametric estimator (\gls{GTLS}, \gls{BTLS}, and \gls{MLE}) is invoked, where the input spectrum is considered to be $1$ at all frequencies (Dirac in the time domain), and the output spectrum is set equal to the estimated \gls{FRF} $G_{\bullet}(\omega_k)$, with the transient term $I$ set to zero:
\begin{equation}
  U_{\mathrm{FRF}}(\omega_k) \isdef 1 
  \qquad \text{and} \qquad
  Y_{\mathrm{FRF}}(\omega_k)  \isdef G_{\bullet}(\omega_k)
  \text{.}
\end{equation}
It is important to note that invoking the \gls{GTLS}, \gls{BTLS} and \gls{MLE} on the \glspl{FRF} from methods 3) and 4) will yield a different result from applying the \gls{GTLS}, \gls{BTLS} and \gls{MLE} on the raw data. 
This is because the \glspl{FRF} from 3) and 4) have been smoothed and, thus, have a significantly reduced noise variance, but might be biased slightly.
\end{remark}

\subsection{Success Rates of the Initial Estimates}
The initial estimates described above are then fed to the \gls{MLE} together with the raw data to obtain the final estimates.

Formally, let $\model{\bullet}$ be the final parametric estimate of the system, where the subscript $\bullet$ denotes the methods (from left to right in Fig.~\ref{fig:flowgraph}) when an initial estimate $\model[init]{\bullet}$ is used, \emph{viz}:
\begin{itemize}
    \item $\model{\trueSymbol}$ via the true model $\true{G}$ as an initial estimate,
    \item $\model{exist}$ is obtained via \gls{GTLS} and \gls{BTLS},
    \item $\model{trunc}$ by the use of the \gls{LPM} with truncation as an initial estimate,
    \item $\model{RFIR}$, initialized by means of the \gls{RFIR} method. 
\end{itemize}

A particular initial estimate is deemed \emph{successful} if the optimization of the \gls{MLE} cost with the raw input-output data inserted in equation~\eqref{eq:MLEcf}, approximately reaches the \emph{best local optimum} when iteration is initiated with the selected initial value/estimate.

@@

Both systems are low-pass Chebyshev filters which have been generated using the \MATLAB command \mcode[mathescape]{cheby1(2, $\,Q$, 0.05)}.
Their transfer functions are shown in \figref{fig:exampleFRF}.
Their inputs are excited by zero mean white Gaussian noise with unit variance, and the outputs are disturbed by different realizations of white gaussian noise, as in \figref{fig:oesetup}, with a variance $\sigma_v^2$, such that a prescribed \gls{SNR} defined as
\begin{equation}
  \mathrm{SNR} 
    = \frac{\sigma_v}
           {\rms{y_0}}
    \approx \frac{\sigma_{v}}
                 {\left\| \true{G} \right\|_2 \rms{u_0}}
    =  \frac{\sigma_{v}}
            {\left\| \true{G} \right\|_2}
  \label{eq:SNR-definition}
  \text{.}
\end{equation}
is attained.
$\rms{x} = \sqrt{N^{-1} \sum_t x^2(t)}$ denotes the root-mean-squared value of $x$.

\subsection{Comparison of Successful and Failed Estimates}
 \figref{fig:exampleFRF} depicts the Bode plot of the actual system $\true{G}$, in black and different estimates $\model{exist}$ that may or may not approximate $\model{\trueSymbol}$ well, according to the distance defined by equation \eqref{eq:successrateTol}.
 The systems shown here are drawn randomly from the successes and failures observed in the Monte Carlo simulations, which are discussed later on in this chapter.

 It is clear from \figref{fig:exampleFRF} that the successful estimates virtually coincide with the true system. 
 This means that their distances from the true system, e.g. as given by $\norm[2]{\model{\bullet} - \true{G}}$, have small values. 
On the other hand, the `failed' estimates are inaccurate descriptions of the true system. 
It is apparent that their associated distances from the true system are larger by, at least, an order of magnitude than for the successful estimates.

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{0.6\figurewidth}
  \input{\thisDir/figs/exampleSystems.tikz}
 \caption[Bodeplot of successful ad failed estimates.]{Illustrative Bode plots of a few successful~\legref{leg:example-good-estimate} and `failed'~\legref{leg:example-bad-estimate} estimates $\model{\bullet}$ for both systems $\true{G}$~\legref{leg:example-exact} under test.
 The `failed' estimates are caused by local minima in the cost function.
 Success or failure is determined using the criterion in equation~\eqref{eq:successrateTol}. The $3\unit{dB}$ bandwidth of each system is highlighted~\legref{leg:example-3db-bandwidth}.}
\label{fig:exampleFRF}
\end{figure}

\subsection{Computation of  the Success Rates}
\label{sec:initial-values:CompuSR}

@@

\subsection{Identification Procedure}
The repeated nature of the experiment makes it possible to estimate the noise level from the signals non-parametrically.
The mean signal from the input $u$ is of the form:
\begin{equation}
  \tilde{u}(t) = \frac{1}{N_R} \sum_{r=1}^{N_R} u^{[r]}(t)
\end{equation}
Thus, the reduced noise influence and the approximate noise co-variances are, respectively:
\begin{align}
  \hat\sigma_{u}^2(t) &= \frac{1}{N_R - 1} 
                    \sum_{r=1}^{N_R} 
                    \left( u^{[r]}(t) - \tilde{u}(t) \right)^2 \\
%and the noise co-variances are approximately
  \hat\sigma_{yu}(t) &= \frac{1}{N_R - 1} 
                    \sum_{r=1}^{N_R} 
                    \left( y^{[r]}(t) - \tilde{y}(t) \right)
                    \overline{\left( u^{[r]}(t) - \tilde{u}(t) \right)}
  \label{eq:variancePeriodic}            
\end{align}

@@

\subsection{Reference Model Measurements}

@@

\subsection{Model Estimation}
  The measurements on the NI Elvis II indicate that the high-quality starting value $G_{\mathrm{VXI}}$ led to low cost function values as shown in \figref{fig:costMeasurements} and \tabref{tbl:costMeasurements}.
  The existing methods exhibit a high spread and a high median cost function, showing that a good estimate is obtained only in about $25\%$ of the cases.
  The truncation method provides better estimates in many cases, but still suffers from a high variability.
  On the other hand, the \gls{RFIR}-based initial values have both a low median cost function and spread, and thus provide better fits in almost all cases.
  Obviously, $\model{best}$ has the lowest cost function values of all methods.
  The similarity of the results for $\model{RFIR}$ and $\model{best}$ suggests that the \gls{RFIR} provides the best estimate in most of the cases.
  This can indeed be confirmed by inspecting the different estimates per repetition of the experiment.

@@

\subsection{Model Validation}
\subsubsection{Cost Function Limitations}
In the previous section, the cost function was studied to determine the effectiveness of the starting values.
However, inspecting the cost function $V(\theta)$ only accounts for how well an estimated model fits the measured data, which may be misleading.
For an example, overfitting a model may result in the absorption of both the systematic behavior and the noise into the model. 
Consequently, an arbitrarily small cost function may ensue although the estimated model may be virtually useless to predict the system behavior.

\subsubsection{Validation Criterion}
To objectively assess the quality of an estimated model, a different criterion than the cost function is inspected.
To this end, the model is validated using the 2-norm (or distance) on the model error:
\begin{equation}
  \validationDistance{\bullet} 
  \isdef 
  \norm[2]{\model{\bullet} - G_{\mathrm{VXI}}}
  \text{.}
  \label{eq:measurementCriterion}
\end{equation} 
This criterion indicates how well the obtained estimates $\model{\bullet}$ are able to describe the transfer function of the bandpass filter as observed in the validation measurement on the \gls{VXI}.

\subsubsection{Validation Performance}
The observed median and \gls{IQR} of the distances in \figref{fig:validationMeasurements} and \tabref{tbl:validationMeasurements} have a similar qualitative interpretation as the cost function on the estimation data.
The existing methods provide good estimates in only $25\%$ of the cases.
The truncation method provides a considerable improvement but still suffers from $25\%$ poor estimates.
Compared to the existing \gls{BTLS} and \gls{GTLS} techniques, the \gls{RFIR} and hence also $\model{best}$ entail an overall reduction in the observed distance by a factor $8$, in most cases. 
On the other hand, the reference $\model{VXI}$ shows the best global performance. 
This indicates that the proposed methods do no converge to the same local optimum.
Nevertheless, the proposed methods improve the model quality by almost an order of magnitude.

@@

\section{Consequences of Selecting the `Best` Model}
To determine how important it is to retain the `best' model based on the cost function values, we shall inspect how much worse (or better) the second best model $\model{2nd}$ performs when $\model{best}$ is \emph{not} selected.
To do so, we inspect the performance by means of the cost function (used during estimation) and by means of the validation distance.
The datasets used in this analysis are those from the measurements, but similar results can be obtained from the other data sets.

@@

\section{Remark on the Generality}
\label{sec:initial-values:Generality}
In the previous sections, the usability of the smoothers to produce initial values has been studied on very specific examples.
In this section, an attempt will be made to illustrate the usefulness of these smoothers for the generation of starting values for other systems.
However, due to the intricate relationship between the attraction regions in the cost function, the location of the actual system poles, the \gls{SNR} level and the choice of a particular excitation signal, we think it is intractable to construct rigid bounds on where the smoothers produce effective starting values.

\subsection{Limitations of the Smoothers}
On the one hand, an obvious limitation to the presented initialization techniques is that they share the limitations of the smoothing techniques: if the non-parametric estimate is a worse representation than the raw data (e.g. heavily biased), it is very unlikely that the initial estimate will outperform the existing estimates.
However, it is beyond the scope of this chapter to determine formally which particular smoother is optimal in some specific experimental circumstances.

@@

\subsection{Stress Test of the Smoothers}
To test the effectiveness of the initial estimates obtained from these particular smoothers, an extra set of $n_{\mathrm{MC}} = 100$ Monte Carlo simulations were performed.
In particular, all combinations of
\begin{itemize}
  \item low-pass, high-pass, band-pass and band-stop 
  \item Chebyshev Type I, Chebyshev Type II, Elliptical and Butterworth
\end{itemize}
discrete-time filters~\citep{Zverev1967} of tenth degree generated by the \MATLAB code in \lstref{lst:initvals:stressSystems} are simulated.
Each of these filters $\true{G}$ have been normalized such that $\norm[2]{\true{G}} = 1$.
The low-pass and high-pass filtes have a cross-over frequency of $\frac{\pi}{2} \unit{rad/s}$. 
The band-pass, respectively band-stop, filters have a passband, respectively stopband, in the frequency range$\left[ \frac{2\pi}{5}, \frac{3\pi}{5}\right] \unit{rad/s}$.
Note also that both the band-pass and band-stop filters have a McMillan degree of 20 as per the \MATLAB conventions.
See \tabref{tbl:init:stresstest} for an overview of the filters and  \figref{fig:bodeplots} for the corresponding bode plots.

@@

\section{Computational Effort}\label{sec:initvals:computation}
While improved initial values yield better models of an improved quality, their generation does require some computational effort.
Although the amount of available computing power has been steadily increasing over the last decades, it remains important to keep an eye on the computing effort required to estimate a model or, in this case, to generate the starting values required to estimate a model.
E.g. in the field of embedded processors, which has been attracting a lot of attention over the last few years leading to ``Internet of Things'', it remains an important factor since computing power and physical power consumption are still relatively scarce.

@@

\subsection{Practical Runtime}
In practical measurements of the computation time for any piece of software, one typically distinguishes between different kinds of `time'.
\begin{itemize}
  \item The wall-clock time $\wallclocktime$, sometimes called `real time`, is the time difference between the start and end of the program under test.
  \item The \glsentryshort{CPU} time $\cputime$, is the amount of time that the \glspl{CPU} actually spends executing the program under test.
\end{itemize}
This distinction is necessary for multi-tasking environments (such as computer), since during the execution of the program under test, the \gls{CPU} may spend a while to execute other programs in the background.
The latter obviously requires a small amount of wall-clock time, but it does not increase the \gls{CPU} time of the program:
\begin{equation}
  \wallclocktime = \cputime + t_{\mathrm{other\;processes}}
\end{equation}
for a single-core \gls{CPU}.

@@

\subsection{Asymptotic Runtime}
For the asymptotic runtime, we are mainly interested in how the runtime of the smoothers scale with the size of the dataset, i.e. the number of samples $N$, and the model complexity $n_{\theta}$ of the smoother.

@@

\subsection{Implementation Aspects}
This section presents some implications and recommendations for the implementation of  a system identification toolbox.

### 2016-05-05 ch06-concl/conclusions.tex
Add thumb index
(sub)+sections: title case + some \gls{...}

\section{Results of this Research}

@@

  \subsection{Non-parametric Estimation}

@@

  \subsection{Non-parametric Estimators}
    The \gls{LRM} has only been explored for \gls{SISO} systems in this thesis.
    This technique can obviously be extended towards \gls{MIMO} systems, e.g. as the work by \citet{vanRietschoten2015MSc} has shown.
    As explored there, the choice of parametrization remains an open question for the \gls{MIMO} case.
    Also, unlike the \gls{SISO} case, it becomes more important and tedious to select good local models since the dimensionality of the local estimation problem grows with the system dimensions.
    Extension to the \gls{MIMO} case, moreover, may directly lead to an approach that is able to deal with concatenated data records similarly to what the \gls{LPM} is able to provide.

@@

  \subsection{Non-parametric Estimation and Interpolation}
  As with the regular \gls{LRM}, ongoing research focusses on the estimation approach of the $\Hinf{}$ gain towards the \gls{MIMO} case.
  In that context, the design of weighting filter also becomes even more important~\citep{Boeren2013}.
  Hence, the link between local models and the design of weighting filters and parametric overbounds is essential and should be confirmed further in a detailed study.

>>>>

\section{Results of This Research}

@@

  \subsection{Non-Parametric Estimation}

@@

  \subsection{Non-Parametric Estimators}
    The \gls{LRM} has only been explored for \gls{SISO} systems in this thesis.
    This technique can obviously be extended towards \gls{MIMO} systems, e.g. as the work by \citet{vanRietschoten2015MSc} has shown.
    As explored there, the choice of parametrization remains an open question for the \gls{MIMO} case.
    Also, unlike the \gls{SISO} case, it becomes more important and tedious to select good local models since the dimensionality of the local estimation problem grows with the system dimensions.
    Extension to the \gls{MIMO} case, moreover, may directly lead to an approach that is able to deal with concatenated data records similarly to what the \gls{LPM} is able to provide.

@@

  \subsection{Non-Parametric Estimation and Interpolation}
  As with the regular \gls{LRM}, ongoing research focusses on the estimation approach of the $\Hinf{}$ gain towards the \gls{MIMO} case.
  In that context, the design of weighting filter also becomes even more important~\citep{Boeren2013}.
  Hence, the link between local models and the design of weighting filters and parametric overbounds is essential and should be confirmed further in a detailed study.
